### 2014-11-13 tex/related.tex

%\subsection{Symbolic Exection}

Recent years have seen a significant growth in research projects based
on symbolic execution, first introduced in the 1970's by
Clarke~\cite{Clarke:76} and King~\cite{King:76}. Initial work on symbolic
execution largely focused on checking properties of program with
primitive types. Several recent projects generalized the core
idea of symbolic execution which enabled it to be applied to
programs with more general types, including references and 
arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during symbolic
execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths
than GSE techniques.

>>>>

While there exists a large body of work related to summary heaps,
we discuss work most closely related, including techniques for
scaling symbolic execution of programs with complex data types,
heap summary techniques, ...

%Recent years have seen a significant growth in research projects based
%on symbolic execution, first introduced in the 1970's by
%Clarke~\cite{Clarke:76} and King~\cite{King:76}.

Initial work on symbolic execution largely focused on checking 
properties of imperative programs with primitive
primitive types~\cite{Clarke:76,King:76}. Several recent projects 
generalized the core
idea of symbolic execution which enabled it to be applied to
programs with more general types, including references and 
arrays~\cite{GSE03,Godefroid:PLDI05,Sen:FSE05,CadarEngler05EXE,KiasanKunit}.
Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during symbolic
execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths
than GSE techniques.
